Guided Proofreading of Automatic Segmentations for Connectomics

### 2017-03-14 paper/evaluation.tex
Add latest changes as discussed with James.

\paragraph{Automatic segmentation pipeline.}
We use a state-of-the-art method to create a dense automatic segmentation of the data. Membrane probabilities are generated using a CNN based on the U-net architecture (trained exclusively on different data than the GP classifiers)~\cite{RonnebergerFB15}. The probabilities are used to seed watershed and generate an oversegmentation using superpixels. Agglomeration is then performed by the GALA active learning classifier with a fixed agglomeration threshold of 0.3~\cite{nunez2014graph}. We further describe this approach in the supplemental material.

@@

\vspace{0.5mm}
\begin{tabular}{ll}
	\toprule
	\begin{tabular}{l}
		\textbf{Focused Proofreading}\\ \midrule
		\emph{Parameters} \\ \midrule
		Iterations: 3 \\
		Learning strategy: 2\\
		Mito agglomeration: Off~~~~~~ \\  % Crappy alignment spacing
		Threshold: 0.0\\
	\end{tabular}
	&
	\begin{tabular}{l}
		\vspace{0.2mm} \\
		\midrule
		\emph{Results---Test Set} \\ \midrule Cost [m]: 217 \\ Test. acc.: 0.99 \\ Prec./Recall: 0.58/0.56 \\ F1 Score: 0.54 \\
	\end{tabular}
%	\bottomrule
\end{tabular}
\hrule
}
\label{tab:parameters}
\end{table}

>>>>

\paragraph{Automatic segmentation pipeline.}
We use a state-of-the-art method to create a dense automatic segmentation of the data. Membrane probabilities are generated using a CNN based on the U-net architecture (trained exclusively on different data than the GP classifiers)~\cite{RonnebergerFB15}. The probabilities are used to seed watershed and generate an oversegmentation using superpixels. Agglomeration is then performed by the GALA active learning classifier with a fixed agglomeration threshold of 0.3~\cite{nunez2014graph}. We describe this approach in the supplemental material.

@@

\vspace{0.5mm}
\begin{tabular}{ll}
	\toprule
	\begin{tabular}{l}
		\textbf{Focused Proofreading}\\ \midrule
		\emph{Parameters} \\ \midrule
		Iterations: 3 \\
		Learning strategy: 2\\
		Mito agglomeration: Off~~~~~~ \\  % Crappy alignment spacing
		Threshold: 0.0\\~\\
	\end{tabular}
	&
	\begin{tabular}{l}
		\vspace{0.2mm} \\
		\midrule
		\emph{Results---Test Set} \\ \midrule Cost [m]: 217 \\ Val. acc.: 0.99 \\ Test. acc.: 0.68 \\ Prec./Recall: 0.58/0.56 \\ F1 Score: 0.54 \\
	\end{tabular}
%	\bottomrule
\end{tabular}
\hrule
}
\label{tab:parameters}
\end{table}

### 2017-03-14 paper/guidedproofreading_review.tex
Results section complete.
Several changes.
Replace merge error image and add timing table.
Switch to ICCV template and update RhoanaNet citation.
Add latest changes as discussed with James.

\usepackage{cvpr}
\usepackage{microtype}
\usepackage{times}
\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{booktabs}
% Include other packages here, before hyperref.

@@

\newcommand{\JT}[1]{\textcolor{blue}{JT: #1}}
\newcommand{\HP}[1]{\textcolor{red}{HP: #1}}

@@

\def\cvprPaperID{0947} % *** Enter the CVPR Paper ID here
\def\httilde{\mbox{\tt\raisebox{-.5ex}{\symbol{126}}}}

% Pages are numbered in submission mode, and unnumbered in camera-ready
\ifcvprfinal\pagestyle{empty}\fi
\begin{document}

@@

%%%%%%%%% ABSTRACT
\begin{abstract}
%
Automatic cell image segmentation methods in connectomics produce merge and
split errors, which require correction through proofreading. Previous research
has identified the visual search for these errors as the bottleneck in
interactive proofreading. To aid error correction, we develop two classifiers
that automatically recommend candidate merge and splits to the user. These
classifiers use a convolutional neural network (CNN) that has been trained with
errors in automatic segmentations against expert-labeled ground truth. Our
classifiers detect potentially-erroneous regions by considering a large context
region around a segmentation boundary. Corrections can then be performed by a
user with yes/no decisions,  which results in faster correction times than previous
proofreading methods. We also present a fully-automatic mode that uses a
probability threshold to make merge/split decisions. Extensive experiments using
the automatic approach and comparing performance of novice and expert users
demonstrate that our method performs favorably against state-of-the-art
proofreading methods on different connectomics datasets.
%
\end{abstract}

>>>>

%\usepackage{cvpr}
\usepackage{iccv}
\usepackage{microtype}
\usepackage{times}
\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{booktabs}
\usepackage{makecell}

% Include other packages here, before hyperref.

@@

\newcommand{\JT}[1]{\textcolor{blue}{JT: #1}}
\newcommand{\HP}[1]{\textcolor{red}{HP: #1}}
\newcommand{\DFH}[1]{\textcolor{red}{DH: #1}}

@@

%\def\cvprPaperID{0947} % *** Enter the CVPR Paper ID here
\def\iccvPaperID{0922}
\def\httilde{\mbox{\tt\raisebox{-.5ex}{\symbol{126}}}}

% Pages are numbered in submission mode, and unnumbered in camera-ready
%\ifcvprfinal\pagestyle{empty}\fi
\ificcvfinal\pagestyle{empty}\fi
\begin{document}

@@

%%%%%%%%% ABSTRACT
\begin{abstract}
%
Automatic cell image segmentation methods in connectomics produce merge and
split errors, which require correction through proofreading. Previous research
has identified the visual search for these errors as the bottleneck in
interactive proofreading. To aid error correction, we develop two classifiers
that automatically recommend candidate merges and splits to the user. These
classifiers use a convolutional neural network (CNN) that has been trained with
errors in automatic segmentations against expert-labeled ground truth. Our
classifiers detect potentially-erroneous regions by considering a large context
region around a segmentation boundary. Corrections can then be performed by a
user with yes/no decisions, which reduces variation of information $7.5\times$ faster than previous
proofreading methods. We also present a fully-automatic mode that uses a
probability threshold to make merge/split decisions. Extensive experiments using
the automatic approach and comparing performance of novice and expert users
demonstrate that our method performs favorably against state-of-the-art
proofreading methods on different connectomics datasets.
%
\end{abstract}

### 2017-03-14 paper/results.tex
Add latest changes as discussed with James.

\begin{table}[h]
\caption{Average proofreading speed for users of Dojo, Focused Proofreading (FP) and our Guided Proofreading (GP). For comparable correction time, our system achieves significantly higher VI reduction per minute (7.5$\times$) over state-of-the-art FP.}%While the training of our classifier is more expensive, testing accuracy is superior. }
\resizebox{\linewidth}{!}{
\begin{tabular}{lrrrr}
\toprule
Approach & \makecell{Time Per Correction (s)} & \makecell{VI Reduction Per Minute} \\
\midrule
\emph{Dojo} & 30.5 & -0.002 \\
%\emph{Dojo Expert?} & xxx & xxx \\
\emph{FP} & 4.9 & 0.00023 \\
\emph{GP} & 6.2 & 0.00173 \\
\bottomrule
\end{tabular} 
}
\label{tab:correctiontimes}
\end{table}

>>>>

\begin{table}[h]
\caption{Average proofreading speed for users of Dojo, Focused Proofreading (FP) and our Guided Proofreading (GP). Our system achieves significantly higher VI reduction per minute (7.5$\times$) over state-of-the-art FP, while being slightly slower per correction.}%While the training of our classifier is more expensive, testing accuracy is superior. }
\resizebox{\linewidth}{!}{
\begin{tabular}{lrrrr}
\toprule
Approach & \makecell{Time Per\\Correction (s)} & \makecell{VI Reduction\\Per Minute} & \makecell{Improvement} \\
\midrule
\emph{Dojo} & 30.5 & -0.00200 & $-8.7\times$ \\
%\emph{Dojo Expert?} & xxx & xxx \\
\emph{FP} & 4.9 & 0.00023 & $1.0\times$\\
\emph{GP} & 6.2 & 0.00173 & $7.5\times$\\
\bottomrule
\end{tabular} 
}
\label{tab:correctiontimes}
\end{table}
